### 2009-04-03 talk/icooolps2009-dotnet/benchmarks.tex
copy the introduction from the ecoop paper, and adapt it to this one. Add few XXXs
minor fixes

@@

When doing plain interpretation, we need to create and destroy three temporary
objects at each iteration.  By contrast, the code generated by the JIT does
much better.  At the first iteration, the classes of the two operands of the
multiplication are promoted; then, the JIT compiler knows that both are
integers, so it can inline the code to compute the result.  Moreover, it can
\emph{virtualize} (see Section \ref{sec:virtuals}) all the temporary objects, because they never escape from
the inner loop.  The same remarks apply to the other two operations inside
the loop.

@@

On the other, for reasonably high values of $n$ we obtain very good
results, which are valid despite the obvious overflow, since the 
same operations are performed for all experiments.
For $n$ greater than $10^7$, we did not run the interpreted program as it would have took too
much time, without adding anything to the discussion.

>>>>

\anto{XXX: we need to give an overview of TLC}

@@

\anto{XXX: explain which temp objects are created}
When doing plain interpretation, we need to create and destroy three temporary
objects at each iteration.  By contrast, the code generated by the JIT does
much better.  At the first iteration, the classes of the two operands of the
multiplication are promoted; then, the JIT compiler knows that both are
integers, so it can inline the code to compute the result.  Moreover, it can
\emph{virtualize} (see Section \ref{sec:virtuals}) all the temporary objects, because they never escape from
the inner loop.  The same remarks apply to the other two operations inside
the loop.

@@

On the other, for reasonably high values of $n$ we obtain very good
results, which are valid despite the obvious overflow, since the 
same operations are performed for all experiments.
For $n$ greater than $10^7$, we did not run the interpreted program as it would have taken too
much time, without adding anything to the discussion.

### 2009-04-03 talk/icooolps2009-dotnet/clibackend.tex
minor fixes

In the pictures of Figure~\ref{flexswitch-fig}, block 5 (highlighted in grey)
corresponds to a flexswitch; initially (picture on the left) 
only block 5, containing the code to restart the JIT compilation,
is connected to the flexswitch; the picture on the right
shows the graph after the first case has been dynamically added to the flexswitch,
by linking block 5 with the freshly created block number 7..

@@

Following an external link whose target is an initial block could also
be easily implemented, by just invoking the corresponding method.
What cannot be easily implemented in CLI is following an external link
whose target is not an initial block; consider, for instance, the
outgoing link of the block dynamically added in the right-hand side
picture of Figure~\ref{flexswitch-fig}. How is it possible to jump into
the middle of a method?

@@

  public uint execute(int value, InputArgs args) {
    for(int i=0; i<numcases; i++)
    if (values[i] == value) {
      return cases[i](0, args);
    }
    return default_blockid;
  }
}
\end{lstlisting}
\end{small}
The mapping from integers values to delegates (pointing to secondary
methods) is just implemented by the two arrays \lstinline{values} and
\lstinline{cases}. Method \lstinline{add_case} extends the mapping
whenever a new case is added to the flexswitch.

>>>>

In the pictures of Figure~\ref{flexswitch-fig}, block 5 (highlighted in grey)
corresponds to a flexswitch; initially (picture on the left) 
only block 6, containing the code to restart the JIT compilation,
is connected to the flexswitch; the picture on the right
shows the graph after the first case has been dynamically added to the flexswitch,
by linking block 5 with the freshly created block number 7.

@@

Following an external link whose target is an initial block could also
be easily implemented, by just invoking the corresponding method.
What cannot be easily implemented in CLI is following an external link
whose target is not an initial block; consider, for instance, the
outgoing link from block 7 to block 3 in Figure~\ref{flexswitch-fig}. How is it possible to jump into
the middle of a method?

@@

  public uint execute(int value, InputArgs args) {
    for(int i=0; i<numcases; i++)
      if (values[i] == value)
        return cases[i](0, args);
    return default_blockid;
  }
}
\end{lstlisting}
\end{small}
The mapping from integers values to delegates (pointing to secondary
methods) is just implemented by the two arrays \lstinline{values} and
\lstinline{cases}. Method \lstinline{add_case} extends the mapping
whenever a new case is added to the flexswitch.
